SAT Competition 2020\tnoteref{title}

### 2021-06-05 paper/main.tex
additional challenges in distributed sat solving

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2}
(see Figure~\ref{fig:res-cloud}).
\solver{Mallob-Mono} was able to solve more instances in 1000 seconds than the 
winner of the Parallel Track in 5000 seconds, which shows the potential of distributed SAT solving. 
The other four participants performed significantly worse. This is likely due to the initial challenges
in developing a distributed solver. 2020 was the first year of this track. We expect this gap to turn smaller in 
forthcoming SAT competitions.

>>>>

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2}
(see Figure~\ref{fig:res-cloud}).
\solver{Mallob-Mono} was able to solve more instances in 1000 seconds than the 
winner of the Parallel Track in 5000 seconds, which shows the potential of distributed SAT solving. 
The other four participants performed significantly worse. 
The massive parallelism in distributed SAT solving imposes additional challanges on scalable information sharing and search diversification. 
Since 2020 was the first year of this track, we expect a tighter competition in the future.
